Numerical Solution of Point Defect(Rate Theory) Equations (in MOOSE)

### 2021-02-12 examples/point_defects/article/article.tex
article-edit

\documentclass[a4paper]{article}
\usepackage[margin=25mm]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage[font=scriptsize]{caption}
\pagenumbering{arabic}
\graphicspath{ {./plots/} }

% Keywords command
\providecommand{\keywords}[1]
{
  \small
  \textbf{\textit{Keywords---}} #1
}

% \tableofcontents

\title{Numerical Solution of Point Defect Equations by MOOSE}
\author{Abdurrahman Ozturk$^{1}$, Author$^{1}$, Author$^{1}$, Karim Ahmed$^{1}$  \\
        \small $^{1}$Texas A\&M University \\
        % \small $^{2}$University B \\
}
% \date{} % Comment this line to show today's date
\begin{document}
\maketitle

@@

We present a detailed investigation of the effect of size on the segregation of point defects to interfaces and the resultant nucleation of voids. We utilize the spatially-resolved rate-theory (SRRT) modeling technique valid for modeling surfaces as discrete sinks. The effects of defect production rate, bias, and profile are thoroughly studied. The model predictions are generally different from the textbook ones obtained by the classical homogenized rate theory approach. The simulations show a strong dependence of the steady state defect profiles on the grain size, temperature, and production rate, bias, and profile. Moreover, the sink strength of each boundary is also affected by these factors. Furthermore, it is predicted that whenever there is a production bias, no neutral sinks can exist, i.e., there is always a preference for surfaces/interfaces to absorb one type of defects over another. The model predictions demonstrate the shortcomings of the classical homogenous rate-theory approach and shed light on the limitations of using ion irradiation to mimic neutron irradiation.

% Irradiation of a material creates point defects, vacancies and interstitials, as a result of
% atomic collisions. Those point defects are mobile and able to diffuse through material, recombine with each other,
% and disappear when they react with sinks. The concentration of both vacancy and interstitial can be described mathematically by chemical rate balance equations, named point defect equations (rate theory equations). Production, recombination, diffusion and reaction of point defects are given by separate terms in those equations, which makes it easy to solve and analyze each of them individually. In this work, spatially resolved non-dimensional point defect equations are solved in 1D by using MOOSE Framework. The effect of irradiation dose rate, sink density, temperature, uniform defect production, non-uniform defect production and biased defect production on steady state defect concentration profile and on grain boundary sink strength are studied. The calculations are also repeated for different grain sizes changing from 5\emph{nm} to 5$\mu$\emph{m} to investigate the effect of grain size on defect concentration and grain boundary sink strength. According to results, the grain size and defect production profile/bias have a significant effect on concentration profiles. They could create a flipped concentration profile through domain, which ends up with a defect segregation near grain boundary.

\end{abstract} \hspace{10pt}

%TC:ignore
\keywords{point defect equations, rate theory, interstitial, vacancy, radiation damage, MOOSE}
%TC:endignore

% Word count
% \verbatiminput{\jobname.wordcount.tex}

% \listoftables
% \listoffigures

\section{Introduction} \hspace{10pt}
\newpage
\section{Methodology} \hspace{10pt}

\subsection{Point Defect Equations} \hspace{10pt}
The irradiation of a material causes the creation of vacancies and interstitial because of
atomic collisions. The point defects can diffuse through material, recombine with each other,
and react with sinks which are present in microstructure. The concentration of point defects is
described mathematically by the chemical rate balance equations given in following sets of equations.\\

\begin{equation}
  \begin{aligned}
    &\frac{dC_i}{dt} = K_0 - K_{iv}C_iC_v - K_{is}C_iC_s + \nabla\cdot D_i\nabla C_i\\
    &\frac{dC_v}{dt} = (1+b)K_0 - K_{iv}C_iC_v - K_{vs}C_vC_s + \nabla\cdot D_v\nabla C_v\\
  \end{aligned}
  \label{equation:point_defect_equations}
\end{equation}\\

There are different terms with different rate coefficients as seen in Eq. \ref{equation:point_defect_equations}. The first term on the RHS is a source term, representing defect generation with rate of \textit{K\textsubscript{0}}. In vacancy equation, \textit{b} is used as percent production bias to create a difference between interstitial and vacancy generation in domain. The second term is a reaction term, referring the recombination process if the defect \textit{x} reacts with defect \textit{y} with a rate of \textit{K\textsubscript{xy}}. The third term is also a reaction term, representing the reaction between the defect \textit{x} and the sink \text{s} with a rate of \textit{K\textsubscript{xs}}. In this study, the sink concentration is assumed constant and uniformly distributed over domain. The last term is diffusion term which is resolving the spatial behavior of defects.\\

Another form of point defect equations can be written by using sink strength, \textit{k} definition for sink reaction term.\\

@@

\subsection{Non-dimensionalization of Point Defect Equations} \hspace{10pt}
The time space of defect interactions is enormously large, which could differ from nanoseconds to hours. In addition, rate coefficients also have different orders. To make it easier to solve point defect equations numerically, their non-dimensionalized forms are implemented in MOOSE. The non-dimensionalization scheme and final form of equations are given in this section.

Scaling factors and non-dimensionalized variables are introduced as,

@@

After substituting Eq. \ref{equation:non-dimensionalization_variables} into \ref{equation:point_defect_equations} and reorganizing, the non-dimensionalized version of point defect equations are,

\begin{equation}
  \begin{aligned}
    &\frac{dX_i}{dt} = \Omega\omega K_0 - \frac{\omega K_{iv}}{\Omega}X_iX_v - \frac{\omega K_{is}}{\Omega}X_iX_s + \omega D_i\nabla^2 X_i\\
    &\frac{dX_v}{dt} = \Omega\omega K_0 - \frac{\omega K_{iv}}{\Omega}X_iX_v - \frac{\omega K_{vs}}{\Omega}X_vX_s + \omega D_v\nabla^2 X_v\\
  \end{aligned}
  \label{equation:non-dimensionalized_point_defect_equations}
\end{equation}\\
or
\begin{equation}
  \begin{aligned}
    &\frac{dX_i}{dt} = \widetilde{K_0} - \widetilde{K_{iv}}X_iX_v - \widetilde{K_{is}}X_iX_s + \widetilde{D_i}\widetilde{\nabla}^2 X_i\\
    &\frac{dX_v}{dt} = \widetilde{K_0} - \widetilde{K_{iv}}X_iX_v - \widetilde{K_{vs}}X_vX_s + \widetilde{D_v}\widetilde{\nabla}^2 X_v\\
  \end{aligned}
  \label{equation:non-dimensionalized_point_defect_equations}
\end{equation}\\

\subsection{Model Settings and Parameters} \hspace{10pt}
Nickel is selected as a base material, and its properties are used in calculations.

\begin{table}[h!]
  \centering
  \caption{Material Properties for Nickel\cite{walgraef1996}}
  \label{table:Ni_material_properties}
  \begin{tabular}{ ||p{2cm}|p{2cm}||  }
     % \hline
     % \multicolumn{5}{|c|}{Material Properties} \\
     \hline
     Property & Value\\
     \hline\hline
     a  & 0.352 nm\\
     V  & 0.01206 nm^3\\
     E_{m,i}  & 0.30 eV\\
     E_{m,v}  & 1.30 eV\\
     E_{f,i}  & 4.27 eV\\
     E_{f,v}  & 1.60 eV\\
     D_{0,i}  & 1e-7 m^2/s\\
     D_{0,v}  & 6e-5 m^2/s\\

     \hline
  \end{tabular}
\end{table}

\begin{table}[h!]
  \centering
  \caption{Simulation Parameters}
  \label{table:simulation_parameters}
  \begin{tabular}{ ||p{2cm}|p{3cm}|p{3cm}|p{3cm}|p{3cm}||  }
     % \multicolumn{5}{|c|}{Simulation Parameters} \\
     \hline
     Type & Dose Rate (dpa/s) & Defect Production & Temperature (K) & Sink Density (m^{-3})\\
     \hline
     \hline
     Neutron  & 1e-3  & Uniform     & 773 & 1e18\\
              & 1e-6  & Uniform     & 773 & 1e18\\
     \hline
     Ion      & 1e-3  & Distributed & 773 & 1e18\\
              & 1e-6  & Distributed & 773 & 1e18\\
     \hline
  \end{tabular}
\end{table}

\newpage
\section{Results} \hspace{10pt}

In reactor environment, materials are exposed to different types of particle radiation such as electron, proton, neutron and ion. This study covers two most significant irradation types, neutrons and ions. The results obtained from MOOSE simulations are presented in this section by plots of defect concentration, vacancy supersaturation and sink strengths. %The calculated sink strengths are also tabulated for different grain size and bias rates.

  \subsection{Neutron Irradiation} \hspace{10pt}
  Neutrons have an energy spectrum that varies a couple of orders of magnitude. This makes defect generation possible at different energies. Also, the high penetration depth of neutrons allow them to travel through material corresponding to their energies. Thus, they cause a uniform or flat-like defect production profile in material.\cite{was2016}

  Numerical models are frequently used to solve scientific problems and make decisions based on results obtained from simulations, but first, the numerical approach should be reliable. Before presenting results from this study, a simple spherical grain problem for neutron irradation is solved by MOOSE as benchmark problem, and its results are compared to analytical results for validation.

  In this approach, unlike the simulations in this study, the mutual recombination term in Eq. \ref{equation:point_defect_equations_sink_strength} is neglected, and the steady state analytical solutions for a spherical grain of radius \textit{a} are found as below.\cite{heald1977}\\

  \begin{equation}
    \begin{aligned}
      &0 = \frac{K_0}{D_i} - k_i^2C_i + \frac{d^2C_i}{dr^2}+\frac{2}{r}\frac{dC_i}{dr}\\
      &0 = \frac{K_0}{D_v} - k_v^2C_v + \frac{d^2C_v}{dr^2}+\frac{2}{r}\frac{dC_v}{dr}\\
    \end{aligned}
    \label{equation:spherical_norecomb_point_defect_equations}
  \end{equation}\\
  \begin{equation}
    \begin{aligned}
      &C_i(r)=\frac{K_0}{D_ik_i^2}\bigg(1-\frac{a\sinh{k_ir}}{r\sinh{k_ia}}\bigg)\\
      &C_v(r)=\frac{K_0}{D_vk_v^2}\bigg(1-\frac{a\sinh{k_vr}}{r\sinh{k_va}}\bigg)\\
    \end{aligned}
    \label{equation:spherical_grain_analytical_solution}
  \end{equation}\\

  This approach is tested in MOOSE by solving point defect concentrations for a spherical grain having radius of 500 nm. As seen in Fig. \ref{figure:concentrations_MOOSE_analytical}, MOOSE results exactly match with the analytical solution, which makes it a useful tool to analyze behavior of defect concentrations.
  \begin{figure}[h!]
    \centering
    \includegraphics[scale=0.55]{concentration_profiles_MOOSE_Analytical_Neutron_0}
    \caption{Comparison of MOOSE results with analytical solution for spherical grain (\textit{a}=500 nm).}
    \label{figure:concentrations_MOOSE_analytical}
  \end{figure}
  \newpage
  \subsubsection{Concentrations} \hspace{10pt}
  The defect concentrations can follow different patterns depending on their properties. Interstitials diffuse to sinks faster than vacancies, so their steady state concentrations becomes lower (see Fig. \ref{figure:average_concentrations_neutron_5}). The effect of grain size and dose rate are shown in the same figure. The effect of grain size on the point defect kinetics resembles to some extent the effect of temperature. This is due to the fact that both factors affect the diffusion kinetics of defects. However, as will be discussed shortly, its effect on the spatial steady-state profiles is even more complex. The dose rate acts like an amplifier and change intensity of the defect behavior, thus the seperation between defect concentrations becomes more explicit.

    \begin{figure}[h!]  %Neutron - average conc - %5 Bias rate
      \centering
      \subfloat{a)\includegraphics[scale=0.55]{average_concentration_neutron_5_size}}
      \qquad
      \subfloat{b)\includegraphics[scale=0.55]{average_concentration_high_neutron_5_size}}
      \caption{Time-dependent behavior of average defect concentration  with 5\% production bias, a)low dose rate neutron, b) high dose rate neutron}
      \label{figure:average_concentrations_neutron_5}
    \end{figure}

@@

    For unbiased case, as a result of uniform defect production and equilibrium condition at boundaries, the concentration profiles are symmetrical around domain center. The steady state concentration at center doesn't change significantly with increasing size as shown in Fig. \ref{figure:concentrations_neutron_0_1e-6}. In case of high dose rate neutron, concentration levels increase at the center of domain with higher gradients close to the boundaries. (see Fig. \ref{figure:concentrations_neutron_0_1e-3}).\\

    \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %0 Bias rate
      \centering
      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-neutron-0}}
      \qquad
      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-0}}
      \caption{Concentration profiles for low dose rate neutron with 0\% production bias, a) interstitial concentration, b) vacancy concentration}
      \label{figure:concentrations_neutron_0_1e-6}
    \end{figure}
    \begin{figure}[h!]  %Neutron - 1e-3 dpa/s - %0 Bias rate
      \centering
      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-high_neutron-0}}
      \qquad
      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-high_neutron-0}}
      \caption{Concentration profiles for high dose rate neutron with 0\% production bias, a) interstitial concentration, b) vacancy concentration}
      \label{figure:concentrations_neutron_0_1e-3}
    \end{figure}
    \newpage
     If production bias (\%5) is applied, the steady state concentration profiles change considerably. The interstitial concentration at center decreases, and its spatial profile turns down after \textit{critical grain size} (${\sim}$1000 nm in Fig. \ref{figure:concentrations_neutron_5_1e-6}a). Moreover, the depth of profile gets larger with increasing grain size, which could be explained as acumulation of more interstitial atoms trying to reach equilibrium at boundary. The vacancy concentration, on the other hand, increases proportional to grain size, and its profile starts having peak at higher concentrations as seen in Fig. \ref{figure:concentrations_neutron_5_1e-6}b.\\
    \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %5 Bias rate
      \centering
      \subfloat{a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-neutron-5}}
      \qquad
      \subfloat{b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-5}}
      \caption{Concentration profiles for low dose rate neutron with 5\% production bias, a) interstitial concentration, b) vacancy concentration}
      \label{figure:concentrations_neutron_5_1e-6}
    \end{figure}\\

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is just an example/guide for you to refer to when submitting manuscripts to Frontiers, it is not mandatory to use Frontiers .cls files nor frontiers.tex  %
% This will only generate the Manuscript, the final article will be typeset by Frontiers after acceptance.
%                                              %
%                                                                                                                                                         %
% When submitting your files, remember to upload this *tex file, the pdf generated with it, the *bib file (if bibliography is not within the *tex) and all the figures.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Version 3.4 Generated 2018/06/15 %%%
%%% You will need to have the following packages installed: datetime, fmtcount, etoolbox, fcprefix, which are normally inlcuded in WinEdt. %%%
%%% In http://www.ctan.org/ you can find the packages and how to install them, if necessary. %%%
%%%  NB logo1.jpg is required in the path in order to correctly compile front page header %%%

\documentclass[utf8]{frontiersSCNS} % for Science, Engineering and Humanities and Social Sciences articles
%\documentclass[utf8]{frontiersHLTH} % for Health articles
%\documentclass[utf8]{frontiersFPHY} % for Physics and Applied Mathematics and Statistics articles

%\setcitestyle{square} % for Physics and Applied Mathematics and Statistics articles
\usepackage{url,hyperref,lineno,microtype,subcaption}
\usepackage[onehalfspacing]{setspace}
\graphicspath{ {./plots/} }

% \linenumbers

% Leave a blank line between paragraphs instead of using \\

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Ozturk {et~al.}} %use et al only if is more than 1 author
\def\Authors{Abdurrahman Ozturk\,$^{1,*}$, Merve Gencturk\,$^{1}$, Karim Ahmed\,$^{1}$}
% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
\def\Address{$^{1}$Department of Nuclear Engineering, Texas A\&M University, USA}
% The Corresponding Author should be marked with an asterisk
% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
\def\corrAuthor{Abdurrahman Ozturk}
\def\corrEmail{aozturk@tamu.edu}

\begin{document}
\onecolumn
\firstpage{1}

\title[Numerical Solution of Rate Theory Equations]{Numerical Solution of Point Defect(Rate Theory) Equations (in MOOSE)}

\author[\firstAuthorLast ]{\Authors} %This field will be automatically populated
\address{} %This field will be automatically populated
\correspondance{} %This field will be automatically populated

\extraAuth{}% If there are more than 1 corresponding author, comment this line and uncomment the next one.
%\extraAuth{corresponding Author2 \\ Laboratory X2, Institute X2, Department X2, Organization X2, Street X2, City X2 , State XX2 (only USA, Canada and Australia), Zip Code2, X2 Country X2, email2@uni2.edu}

\maketitle

@@

%%% Leave the Abstract empty if your article does not require one, please see the Summary Table for full details.
\section{}
We present a detailed investigation of the effect of size on the segregation of point defects to interfaces and the resultant nucleation of voids. We utilize the spatially-resolved rate-theory (SRRT) modeling technique valid for modeling surfaces as discrete sinks. The effects of defect production rate, bias, and profile are thoroughly studied. The model predictions are generally different from the textbook ones obtained by the classical homogenized rate theory approach. The simulations show a strong dependence of the steady state defect profiles on the grain size, temperature, and production rate, bias, and profile. Moreover, the sink strength of each boundary is also affected by these factors. Furthermore, it is predicted that whenever there is a production bias, no neutral sinks can exist, i.e., there is always a preference for surfaces/interfaces to absorb one type of defects over another. The model predictions demonstrate the shortcomings of the classical homogeneous rate-theory approach and shed light on the limitations of using ion irradiation to mimic neutron irradiation.

\tiny
 \keyFont{ \section{Keywords:} point defect equations, rate theory, interstitial, vacancy, radiation damage, MOOSE} %All article types: you may provide up to 8 keywords; at least 5 are mandatory.
\end{abstract}

\section{Introduction}

\textcolor{red}{
-articles about neutron, proton, ion irradiation\\
radiation damage/interactions//
motivation about paper//
Harsh conditions//
neutron-ion case comparison//
instabilities, extended defects (Ghoniem paper)//
in this study, focusing effect of grain size, bias, discrete surfaces,
homogenized RT, spatially resolution//
qualifying extended defects//
profiles change with increasing radiation damage
}
% For Original Research Articles \citep{conference}, Clinical Trial Articles \citep{article}, and Technology Reports \citep{patent}, the introduction should be succinct, with no subheadings \citep{book}. For Case Reports the Introduction should include symptoms at presentation \citep{chapter}, physical exams and lab results \citep{dataset}.

\section{Methodology}

% For requirements for a specific article type please refer to the Article Types on any Frontiers journal page. Please also refer to  \href{http://home.frontiersin.org/about/author-guidelines#Sections}{Author Guidelines} for further information on how to organize your manuscript in the required sections or their equivalents for your field

% For Original Research articles, please note that the Material and Methods section can be placed in any of the following ways: before Results, before Discussion or after Discussion.

\subsection{Point Defect Equations}
    The irradiation of a material causes the creation of vacancies and interstitial because of atomic collisions. The point defects can diffuse through material, recombine with each other, and react with sinks which are present in microstructure. The concentration of point defects is described mathematically by the chemical rate balance equations given in following sets of equations.

\begin{equation}
  \begin{aligned}
    &\frac{dC_i}{dt} = K_0 - K_{iv}C_iC_v - K_{is}C_iC_s + \nabla\cdot D_i\nabla C_i\\
    &\frac{dC_v}{dt} = (1+b)K_0 - K_{iv}C_iC_v - K_{vs}C_vC_s + \nabla\cdot D_v\nabla C_v
  \end{aligned}
  \label{equation:point_defect_equations}
\end{equation}

    There are different terms with different rate coefficients as seen in Eq. \ref{equation:point_defect_equations}. The first term on the RHS is a source term, representing defect generation with rate of \textit{K\textsubscript{0}}. In vacancy equation, \textit{b} is used as percent production bias to create a difference between interstitial and vacancy generation in domain. The second term is a reaction term, referring the recombination process if the defect \textit{x} reacts with defect \textit{y} with a rate of \textit{K\textsubscript{xy}}. The third term is also a reaction term, representing the reaction between the defect \textit{x} and the sink \textit{s} with a rate of \textit{K\textsubscript{xs}}. In this study, the sink concentration is assumed constant and uniformly distributed over domain. The last term is diffusion term which is resolving the spatial behavior of defects.\\
    Another form of point defect equations can be written by using sink strength, \textit{k} definition for sink reaction term.

@@

\subsection{Non-dimensionalization of Point Defect Equations}
    The time space of defect interactions is enormously large, which could differ from nanoseconds to hours. Additionally, reaction rate coefficients also have different orders of magnitude. To deal with inconsistent dimensions, non-dimensionalized form of equations can be considered for numerical solution. To that end, the following non-dimensionalization scheme and scaling factors are introduced.

@@

    After substituting Eq. \ref{equation:non-dimensionalization_variables} into \ref{equation:point_defect_equations} and reorganizing, final form  of non-dimensionalized point defect equations become,

    \begin{equation}
      \begin{aligned}
        &\frac{dX_i}{dt} = \Omega\omega K_0 - \frac{\omega K_{iv}}{\Omega}X_iX_v - \frac{\omega K_{is}}{\Omega}X_iX_s + \omega D_i\nabla^2 X_i\\
        &\frac{dX_v}{dt} = \Omega\omega K_0 - \frac{\omega K_{iv}}{\Omega}X_iX_v - \frac{\omega K_{vs}}{\Omega}X_vX_s + \omega D_v\nabla^2 X_v\\
      \end{aligned}
      \label{equation:non-dimensionalized_point_defect_equations}
    \end{equation}\\
    or
    \begin{equation}
      \begin{aligned}
        &\frac{dX_i}{dt} = \widetilde{K_0} - \widetilde{K_{iv}}X_iX_v - \widetilde{K_{is}}X_iX_s + \widetilde{D_i}\widetilde{\nabla}^2 X_i\\
        &\frac{dX_v}{dt} = \widetilde{K_0} - \widetilde{K_{iv}}X_iX_v - \widetilde{K_{vs}}X_vX_s + \widetilde{D_v}\widetilde{\nabla}^2 X_v\\
      \end{aligned}
      \label{equation:non-dimensionalized_point_defect_equations}
    \end{equation}

    The Multiphysics Object-Oriented Simulation Environment (MOOSE) is used as tool to solve point defect equations numerically. MOOSE is an open-source framework that provides users to solve partial differential equations (PDEs) and build a state-of-the-art, computationally scalable finite element-based simulations. \textcolor{red}{ref.}\\

\subsection{Model Settings and Parameters}
    Ni-based alloys have been used in many nuclear reactors applications because of their excellent corrosion resistance and high mechanical properties. For example, Ni-based alloys containing 15-30\% Cr are generally used in reactor cooling systems due to their corrosion resistance. However, their properties change under irradiation and needs to be investigated. \textcolor{red}{irradiation induced embrittlement, phase instability, and swelling. It is essential to predict the material structure changes due to radiation accurately.} \citep{walgraef1996}

    \textcolor{blue}{
    Nickel is selected as base material for this study, and its properties; lattice parameter, $a$, is 0.352 $nm$, atomic volume, $V$, is 0.01206 $nm^3$, migration energy for interstitial, $E_{m,i}$, is 0.30 $eV$, migration energy for vacancy, $E_{m,v}$, is 1.30 $eV$, formation energy for interstitial, $E_{f,i}$, is 4.27 $eV$, formation energy for vacancy, $E_{f,v}$, is 1.60 $eV$, diffusion coefficient for interstitial, $D_{0,i}$, is 1e-7 $m^2/s$, and diffusion coefficient for vacancy, $D_{0,v}$, is 6e-5 $m^2/s$.
    \citep{ref}
    }\\

    \textcolor{blue}{
    In this study, three different irradiation types, neutrons, protons and ions, are considered. Their simulations are categorized into two groups based on defect production profile; uniform and non-uniform defect production. Neutrons are highly penetrable and causes uniform defect production on target material. Protons are not able to penetrate as much as neutrons do, but for small domain sizes, their defect production can be assumed as uniform. Ions or heavy charged particles loose their energies quickly and cause a non-uniform defect production. Table \ref{table:simulation_parameters} shows simulation parameters and values.
    }
    \begin{table}[h!]
      \caption{Simulation Parameters}
      \label{table:simulation_parameters}
      \begin{tabular}{ ||>{\centering\arraybackslash}p{3.5cm}|>{\centering\arraybackslash}p{2cm}|>{\centering\arraybackslash}p{3cm}|>{\centering\arraybackslash}p{3cm}|>{\centering\arraybackslash}p{3.5cm}||  }
         % \multicolumn{5}{|c|}{Simulation Parameters} \\
         \hline
         Defect Production & Type & Dose Rate (dpa/s) & Temperature (K) & Sink Density (m^{-3})\\
         \hline
         \hline
         Uniform     & Neutron  & 1e-6  & 773 & 1e18\\
                     & Proton   & 1e-3  & 773 & 1e18\\
         \hline
         Non-Uniform & Ion      & 1e-3  & 773 & 1e18\\
         % Distributed &           & 1e-6  & 773 & 1e18\\
         \hline
      \end{tabular}
    \end{table}

% \textcolor{red}{
% Hoca, bu type neutron,ion kısım için neutron case de high dose rate için proton diyerek ekleyebiliriz bu kısmı tartışalım dedi. Apo'nun yazdığı kısmı etkileyecek hocam apo ile beraber tekrar tartışalım dedim. Bu kısmı sorarız tekrar.
% }

% \textcolor{red}{
% Tables should be inserted at the end of the manuscript. Please build your table directly in LaTeX.Tables provided as jpeg/tiff files will not be accepted. Please note that very large tables (covering several pages) cannot be included in the final PDF for reasons of space. These tables will be published as \href{http://home.frontiersin.org/about/author-guidelines#SupplementaryMaterial}{Supplementary Material} on the online article page at the time of acceptance. The author will be notified during the typesetting of the final article if this is the case.
% }

\section{Results}

    Regarding cost and time, it can be understood that ion radiation has been used for a long time in experimental studies. However, with the development of reactor designs and the increase of long-term licensed reactors, it has been necessary to search for more reliable materials that can operate for a long time under extreme conditions. Therefore, it is essential to investigate the effects of neutron irradiation and ion irradiation in microstructure to determine the equality of neutron and ion irradiation results.

    The results obtained from MOOSE simulations are presented in this section by plots of defect concentration, vacancy supersaturation and sink strengths. The equations are solved in one direction using Lagrange elements and a second-order time integration scheme. In this work, the surfaces represent free surfaces or grain boundaries.\\ %The calculated sink strengths are also tabulated for different grain size and bias rates.

\subsection{Uniform Irradiation}
    Neutrons have an energy spectrum that varies a couple of orders of magnitude. This makes defect generation possible at different energies. Also, the high penetration depth of neutrons allow them to travel through material corresponding to their energies. Thus, they cause a uniform or flat-like defect production profile in material. \citep{was2017}

    Numerical models are frequently used to solve scientific problems and make decisions based on results obtained from simulations, but first, the numerical approach should be reliable. Before presenting results from this study, a simple spherical grain problem for neutron irradiation is solved by MOOSE as benchmark problem, and its results are compared to analytical results for validation.

    In this approach, unlike the simulations in this study, the mutual recombination term in Eq. \ref{equation:point_defect_equations_sink_strength} is neglected, and the steady state analytical solutions for a spherical grain of radius \textit{a} are found as below. \citep{heald1977}\\

    \begin{equation}
        \begin{aligned}
          &0 = \frac{K_0}{D_i} - k_i^2C_i + \frac{d^2C_i}{dr^2}+\frac{2}{r}\frac{dC_i}{dr}\\
          &0 = \frac{K_0}{D_v} - k_v^2C_v + \frac{d^2C_v}{dr^2}+\frac{2}{r}\frac{dC_v}{dr}\\
        \end{aligned}
        \label{equation:spherical_norecomb_point_defect_equations}
    \end{equation}\\

    \begin{equation}
        \begin{aligned}
          &C_i(r)=\frac{K_0}{D_ik_i^2}\bigg(1-\frac{a\sinh{k_ir}}{r\sinh{k_ia}}\bigg)\\
          &C_v(r)=\frac{K_0}{D_vk_v^2}\bigg(1-\frac{a\sinh{k_vr}}{r\sinh{k_va}}\bigg)\\
        \end{aligned}
        \label{equation:spherical_grain_analytical_solution}
    \end{equation}\\

    This approach is tested in MOOSE by solving point defect concentrations for a spherical grain having radius of 500 nm. As seen in Fig. \ref{figure:concentrations_MOOSE_analytical}, MOOSE results exactly match with the analytical solution, which makes it a useful tool to analyze behavior of defect concentrations.\\

    \begin{figure}[h!]
        \centering
        \includegraphics[scale=0.55]{concentration_profiles_MOOSE_Analytical_Neutron_0}
        \caption{Comparison of MOOSE results with analytical solution for spherical grain (\textit{a}=500 nm).}
        \label{figure:concentrations_MOOSE_analytical}
    \end{figure}

 \subsubsection{Concentrations}
    The defect concentrations can follow different patterns depending on their properties. Interstitials diffuse to sinks faster than vacancies, so their steady-state concentrations become lower (see Fig. \ref{figure:average_concentrations_neutron_5}). The effect of grain size and dose rate are shown in the same figure. The effect of grain size on the point defect kinetics resembles to some extent the effect of temperature. This is due to the fact that both factors affect the diffusion kinetics of defects. However, as will be discussed shortly, its effect on the steady-state spatial profiles is even more complicated. The dose rate acts as an amplifier and changes the intensity of the defect behavior. Thus the separation between defect concentrations becomes more explicit.

\textcolor{red}{
instability (flipping) affects the steady state concentrations levels//
abnormal concentration behaviors for both transient(proposed in papers) steady state(observed in this study)//
with grain size increase, defect concentrations diverges. this might initiate problems for physical properties, mechanical properties//
less recombination, more vacancy more void more swelling
}

    \begin{figure}[h!]  %Neutron - average conc - %5 Bias rate
        \centering
        a)\includegraphics[scale=0.55]{average_concentration_neutron_5_size}
        \qquad
        b)\includegraphics[scale=0.55]{average_concentration_high_neutron_5_size}
        \caption{Time-dependent behavior of average defect concentration for different grain sizes with 5\% production bias for a) neutrons and b) protons}
        \label{figure:average_concentrations_neutron_5}
    \end{figure}

@@

    Uniform defect production and equilibrium condition at boundaries result in a symmetrical concentration profile around the domain center for neutron case. The steady-state concentrations at the center doesn't change significantly with increasing size, as shown in Fig. \ref{figure:concentrations_neutron_0_1e-6}.

    Protons tend to create more defect on material, and consequently concentration levels are higher compared to neutrons.(see Fig. \ref{figure:concentrations_neutron_0_1e-3}).

    % \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %0 Bias rate
    %     \centering
    %     a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-neutron-0}
    %     b)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-high_neutron-0}
    %     c)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-0}
    %     d)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-high_neutron-0}
    %     \caption{Concentration profiles with 0\% production bias, interstitial concentration for a) neutrons and b) protons, vacancy concentration for c) neutrons and b) protons}
    %     \label{figure:concentrations_neutron_0_1e-6}
    % \end{figure}

    Whenever a production bias exists, the steady-state profiles of defects show different trends. Depending on production rate and bias, a critical grain size exists above which the spatial dependence of the interstitial, the defect type with lower production rate, is reversed. This result can be attributed to the fact that production bias breaks the symmetry of the point defect balance leading to the manifestation of distinct steady-state profiles for the different defects. It is worth noting that such instability will make irradiation damage more pronounced.
    Since it will enhance the clustering of different point defects into distinct extended defects, vacancies at the center of the domain will cluster into voids. Simultaneously, interstitials close to the boundaries will form dislocation loops.
    In (\%5) production bias case, we have observed that the steady-state concentration profile has changed significantly. The interstitial concentration at center decreases, and its spatial profile turns down after \textit{critical grain size} (${\sim}$1000 nm in Fig. \ref{figure:concentrations_neutron_5_1e-6}a). Moreover, the depth of profile gets larger with increasing grain size, which could be explained as accumulation of more interstitial atoms trying to reach equilibrium at boundary. On the other hand, the vacancy concentration increases equivalent to grain size, as seen in Fig. \ref{figure:concentrations_neutron_5_1e-6}b.

    Similar to the unbiased case, protons increases average concentration levels. The most significant effect of protons is causing decrease in critical grain size. Therefore, the interstitial concentration profile starts being reversed in smaller grain sizes than 500 nm. (see Fig. \ref{figure:concentrations_proton_5_1e-3}).\\
    \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %5 Bias rate
        \centering
        a)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-neutron-5}
        b)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-neutron-5}
        c)\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-high_neutron-5}
        d)\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-high_neutron-5}
        e)\includegraphics[scale=0.55]{average_concentration_250nm}
        f)\includegraphics[scale=0.55]{interstitial_concentration_time_evolution_250nm}
        \caption{Concentration profiles with 5\% production bias for neutrons (a,b) and protons (c,d). e) Average defect concentration change with time for ${250nm}$. f) The evolution of interstitial concentration profile for ${250nm}$}
        \label{figure:concentrations_neutron_5_1e-6}
    \end{figure}\\
